---
title: 'Supplemental for Bayesian Functional Clustering'
date: '`r format(Sys.time(), "%d %B, %Y")`'
output:
  bookdown::html_document2:
    includes:
      in_header: header.html
---

<style>
.fold-btn { 
  float: right; 
  margin: 5px 5px 0 0;
}
.fold { 
  border: 1px solid black;
  min-height: 40px;
}
</style>

<script type="text/javascript">
$(document).ready(function() {
  $folds = $(".fold");
  $folds.wrapInner("<div class=\"fold-blck\">"); // wrap a div container around content
  $folds.prepend("<button class=\"fold-btn\">Unfold</button>");  // add a button
  $(".fold-blck").toggle();  // fold all blocks
  $(".fold-btn").on("click", function() {  // add onClick event
    $(this).text($(this).text() === "Fold" ? "Unfold" : "Fold");  // if the text equals "Fold", change it to "Unfold"or else to "Fold" 
    $(this).next(".fold-blck").toggle("linear");  // "swing" is the default easing function. This can be further customized in its speed or the overall animation itself.
  })
});
</script>

```{r setup, include=FALSE, message = FALSE}
knitr::opts_chunk$set(echo = TRUE)
ipak <- function(pkg){
    new.pkg <- pkg[!(pkg %in% installed.packages()[, "Package"])]
    if (length(new.pkg))
        install.packages(new.pkg, dependencies = TRUE)
    sapply(pkg, require, character.only = TRUE, quietly = TRUE)
    invisible(NULL)
}
ipak(c("pracma", "ineq", "fdasrvf", "tidyverse" ,"REAT", "usmap",
       "DT", "data.table", "furrr", "parallel", "future"))
```

This document replicates figures and tables for both simulation study and
real data analysis results in the manuscript
**Bayesian Spatial Homogeneity Pursuit of Functional Data: an Application to
the U.S. Income Distribution**.

# Replication for Figures

Figures 1-5 and 7-9 are replicated in this section.


(ref:lorenzdata) (a) Lorenz curve calculated based on PUMS 2017 Household Income
data on the national level and for two selected states; (b) Lorenz curves for
all U.S. states.


```{r fig.align='center', fig.width=8, fig.height=4.5, fig.cap="(ref:lorenzdata)"}
load("income_data.Rdata")
source("./MFM_code_norm_diag.R")
source("./helpers.R")

par(mfrow = c(1,2))
lorenz(data$data.HINCP,  bg.col = "white", lctitle = "(a)")
## Utah
lorenz(data$data.HINCP[data$data.ST == 49], lctitle = "", bg.col = "white",
       lc.col =  "#E69F00", add.lc = TRUE, ltype = "dashed")
## New York
lorenz(data$data.HINCP[data$data.ST == 36], lctitle = "", bg.col = "white",
       lc.col = "#56B4E9", add.lc = TRUE, ltype = "longdash")
legend(0, 1, legend = c("National", "Utah", "New York"),
       col = c("black", "#E69F00", "#56B4E9"),
       lty = c("solid", "dashed", "longdash"))

lorenz(data$data.HINCP, lctitle = "(b)", bg.col = "white")
for (i in unique(data$data.ST)) {
  lorenz(data$data.HINCP[data$data.ST == i], lctitle = "", bg.col = "white",
         lc.col =  "grey", add.lc = TRUE, ltype = "dashed")
}
lorenz(data$data.HINCP, lctitle = "", bg.col = "white", add.lc = TRUE)
```

```{r echo=FALSE}
par(mfrow = c(1,1))
```

(ref:simdesign1) Illustration of the first simulation design with three true
clusters, with the first cluster having two disjoint components.

```{r fig.align='center', fig.cap = "(ref:simdesign1)"}
cbPalette <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")
stateinfo <- readRDS("state_fips_name.rds")
c1 <- c("AK", "HI", "CA", "OR", "WA", "ID", "NV", "AZ", "UT", "MT",
        "WY", "ME", "NH", "VT", "NY", "CT", "MA", "RI", "PA", "DE",
        "DC", "MD", "VA", "NC", "WV", "NJ", "SC", "OH")
c2 <- c("ND", "SD", "MN", "IA", "WI", "MI", "IL", "IN", "MO", "KS",
        "NE", "CO")
c3 <-  setdiff(stateinfo$abbr, c(c1, c2))
stateinfo$cluster <- as.factor(1 * (stateinfo$abbr %in% c1) + 
  2 * (stateinfo$abbr %in% c2))
plot_usmap(data = stateinfo, values = "cluster", labels = TRUE) +
  scale_fill_manual(values = cbPalette, name = "Cluster")
```

(ref:simdesign2) Illustration of the second simulation design with three
clusters.

```{r fig.align='center', fig.cap = "(ref:simdesign2)"}
c1 <- c("CA", "WA", "OR", "NV", "AZ", "UT", "ID", "MT", "WY", "CO",
        "TX", "OK", "KS", "NM", "AK", "HI", "NE")
c2 <- c("ND", "SD", "MN", "IA", "MO", "AR", "LA", "MS", "AL", "TN",
        "KY", "IL", "WI", "MI", "IN", "GA", "FL")
c3 <- c("OH", "SC", "NC", "WV", "VA", "MD", "DC", "PA", "DE",
        "NJ", "NY", "CT", "RI", "MA", "NH", "ME", "VT")
stateinfo$cluster <- as.factor(1 * (stateinfo$abbr %in% c1) + 
  2 * (stateinfo$abbr %in% c2) + 3 * (stateinfo$abbr %in% c3))
plot_usmap(data = stateinfo, values = "cluster", labels = TRUE) +
  scale_fill_manual(values = cbPalette, name = "Cluster")
```


(ref:histgini) Histogram of Gini indices for statewise income data (5,100 in
each panel from 100 replicates) for weak and strong signals for the two true cluster designs.

```{r fig.align='center', fig.cap="(ref:histgini)", message=FALSE,fig.height=3.5, fig.width=7, results = "hide"}


N_SIMU_REPS <- 2
N_MAX_ITER <- 500
N_STATES <- 51

#### design 1

c1 <- c("AK", "HI", "CA", "OR", "WA", "ID", "NV", "AZ", "UT", "MT",
        "WY", "ME", "NH", "VT", "NY", "CT", "MA", "RI", "PA", "DE",
        "DC", "MD", "VA", "NC", "WV", "NJ", "SC", "OH")
c2 <- c("ND", "SD", "MN", "IA", "WI", "MI", "IL", "IN", "MO", "KS", "NE", "CO")
c3 <-  setdiff(stateinfo$abbr, c(c1, c2))


cc1 <- which(stateinfo$abbr %in% c1)
cc2 <- which(stateinfo$abbr %in% c2)
cc3 <- which(stateinfo$abbr %in% c3)

IND1 <- 1 * (stateinfo$abbr %in% c1) + 2 * (stateinfo$abbr %in% c2) + 
  3 * (stateinfo$abbr %in% c3)


design1weak <- purrr::map(1:N_SIMU_REPS, ~genData(.x, 0.1, "weak")) 
design1weakGini <- map_dfc(design1weak, ~.x$gini)

design1strong <- purrr::map(1:N_SIMU_REPS, ~genData(.x, 0.1, "strong"))
design1strongGini <- map_dfc(design1strong, ~.x$gini)

design1weakGini$Cluster <- design1strongGini$Cluster <- factor(IND1)

rm(cc1, cc2, cc3, c1, c2, c3, IND)
#### design 2

c1 <- c("CA", "WA", "OR", "NV", "AZ", "UT", "ID", "MT", "WY", "CO",
        "TX", "OK", "KS", "NM", "AK", "HI", "NE")

c2 <- c("ND", "SD", "MN", "IA", "MO", "AR", "LA", "MS", "AL", "TN",
        "KY", "IL", "WI", "MI", "IN", "GA", "FL")

c3 <- c("OH", "SC", "NC", "WV", "VA", "MD", "DC", "PA", "DE",
        "NJ", "NY", "CT", "RI", "MA", "NH", "ME", "VT")



cc1 <- which(stateinfo$abbr %in% c1)
cc2 <- which(stateinfo$abbr %in% c2)
cc3 <- which(stateinfo$abbr %in% c3)

IND2 <- 1 * (stateinfo$abbr %in% c1) + 2 * (stateinfo$abbr %in% c2) + 
  3 * (stateinfo$abbr %in% c3)


design2weak <- purrr::map(1:N_SIMU_REPS, ~genData(.x, 0.1, "weak")) 
design2weakGini <- map_dfc(design2weak, ~.x$gini)

design2strong <- purrr::map(1:N_SIMU_REPS, ~genData(.x, 0.1, "strong"))
design2strongGini <- map_dfc(design2strong, ~.x$gini)


design2weakGini$Cluster <- design2strongGini$Cluster <- factor(IND2)



dataList <- list(design1weakGini, design1strongGini,
                 design2weakGini, design2strongGini)
dataList <- map(dataList, ~reshape2::melt(.x, id.vars = "Cluster"))


df <- plyr::ldply(dataList, data.frame) %>%
  dplyr::select(value, Cluster) %>% mutate(Setting = rep(c(1,2), each = N_STATES * N_SIMU_REPS * 2)) %>%
  mutate(Signal = rep( rep(c("Weak", "Strong"), each = N_STATES * N_SIMU_REPS), 2)) %>%
  mutate(Setting = paste0("Design ", Setting)) %>%
  mutate(Signal = factor(Signal, levels = c("Weak",  "Strong")))

df %>% ggplot(aes(x = value)) + geom_histogram(col = "black", fill = "white") + 
  facet_grid(Setting ~ Signal, scales = "free_x") + theme_bw() + ylab("Count") +
  xlab("Value of Gini index")
```




```{r echo=FALSE, message=FALSE, results='hide', warning = FALSE, message = FALSE}

distance <- readRDS("./USgdist.rds")
distance[distance > 1000] <- 10000

c1 <- c("AK", "HI", "CA", "OR", "WA", "ID", "NV", "AZ", "UT", "MT",
        "WY", "ME", "NH", "VT", "NY", "CT", "MA", "RI", "PA", "DE",
        "DC", "MD", "VA", "NC", "WV", "NJ", "SC", "OH")
c2 <- c("ND", "SD", "MN", "IA", "WI", "MI", "IL", "IN", "MO", "KS", "NE", "CO")
c3 <-  setdiff(stateinfo$abbr, c(c1, c2))


cc1 <- which(stateinfo$abbr %in% c1)
cc2 <- which(stateinfo$abbr %in% c2)
cc3 <- which(stateinfo$abbr %in% c3)

IND1 <- 1 * (stateinfo$abbr %in% c1) + 2 * (stateinfo$abbr %in% c2) + 
  3 * (stateinfo$abbr %in% c3)


sim1 <- function(seed, strength = c("weak", "strong")) {
  set.seed(seed)
  dataset <- genData(seed, 0.1, signal = strength)
  inner_prod_matrix <- dataset$inner_prod_matrix
  n <- nrow(inner_prod_matrix)
  A <- log((inner_prod_matrix - min(inner_prod_matrix)) / (max(inner_prod_matrix) -
                                                          inner_prod_matrix))
  A[which(A == Inf)]  <- max(A[which(is.finite(A) == T)])
  A[which(A == -Inf)] <- min(A[which(is.finite(A) == T)])
  AAA <- A; AAA[lower.tri(AAA)] <- 0
  
  fit1 <- CDMFM(data = A, data1 = AAA, lambda1 = 0.5, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit2 <- CDMFM(data = A, data1 = AAA, lambda1 = 1, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit3 <- CDMFM(data = A, data1 = AAA, lambda1 = 1.5, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit4 <- CDMFM(data = A, data1 = AAA, lambda1 = 2, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit5 <- CDMFM(data = A, data1 = AAA, lambda1 = 0, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  return(list(fit1 = fit1, fit2 = fit2, fit3 = fit3, fit4 = fit4, fit5 = fit5,
            srvf = dataset$srvf))
}


plan(multisession(workers = detectCores() - 1))
## .progress = TRUE will only print progress bars when code in this file is
## executed in interactive mode
design1weakResult <- future_map(1:N_SIMU_REPS, ~sim1(.x, strength = "weak"),
                                .progress = TRUE)
design1weakSummary <- summary_output1(design1weakResult)

design1strongResult <- future_map(1:N_SIMU_REPS, ~sim1(.x, strength = "strong"),
                                  .progress = TRUE)
design1strongSummary <- summary_output1(design1strongResult)


#########################################################################
#########################################################################

c1 <- c("CA", "WA", "OR", "NV", "AZ", "UT", "ID", "MT", "WY", "CO",
        "TX", "OK", "KS", "NM", "AK", "HI", "NE")

c2 <- c("ND", "SD", "MN", "IA", "MO", "AR", "LA", "MS", "AL", "TN",
        "KY", "IL", "WI", "MI", "IN", "GA", "FL")

c3 <- c("OH", "SC", "NC", "WV", "VA", "MD", "DC", "PA", "DE",
        "NJ", "NY", "CT", "RI", "MA", "NH", "ME", "VT")



cc1 <- which(stateinfo$abbr %in% c1)
cc2 <- which(stateinfo$abbr %in% c2)
cc3 <- which(stateinfo$abbr %in% c3)

IND2 <- 1 * (stateinfo$abbr %in% c1) + 2 * (stateinfo$abbr %in% c2) + 
  3 * (stateinfo$abbr %in% c3)

sim2 <- function(seed, strength = c("weak", "strong")) {
  set.seed(seed)
  dataset <- genData(seed, 0.1, signal = strength)
  inner_prod_matrix <- dataset$inner_prod_matrix
  n <- nrow(inner_prod_matrix)
  A <- log((inner_prod_matrix - min(inner_prod_matrix)) / (max(inner_prod_matrix) -
                                                          inner_prod_matrix))
  A[which(A == Inf)]  <- max(A[which(is.finite(A) == T)])
  A[which(A == -Inf)] <- min(A[which(is.finite(A) == T)])
  AAA <- A; AAA[lower.tri(AAA)] <- 0
  
  fit1 <- CDMFM(data = A, data1 = AAA, lambda1 = 1.5, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = N_MAX_ITER, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit2 <- CDMFM(data = A, data1 = AAA, lambda1 = 2, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit3 <- CDMFM(data = A, data1 = AAA, lambda1 = 2.5, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit4 <- CDMFM(data = A, data1 = AAA, lambda1 = 3, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  fit5 <- CDMFM(data = A, data1 = AAA, lambda1 = 0, neighbour = 3,
                    distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
                    mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
                    LAMBDA = 1, initNClusters = 9)
  return(list(fit1 = fit1, fit2 = fit2, fit3 = fit3, fit4 = fit4, fit5 = fit5,
            srvf = dataset$srvf))
}

design2weakResult <- future_map(1:N_SIMU_REPS, ~sim2(.x, "weak"),
                                .progress = TRUE)
design2weakSummary <- summary_output2(design2weakResult)

design2strongResult <- future_map(1:N_SIMU_REPS, ~sim2(.x, "strong"),
                                  .progress = TRUE)
design2strongSummary <- summary_output2(design2strongResult)

p1data <- rbind(design1weakSummary$finalK, design1strongSummary$finalK) %>%
  mutate(Signal = rep(c("Weak", "Strong"), each = 5 * N_SIMU_REPS))
p1data$Signal <-  factor(p1data$Signal, levels = c("Weak", "Strong"),
                         labels = c("Weak", "Strong"))
p1 <- p1data %>% ggplot(aes(x = count)) + 
  geom_histogram(binwidth = 0.5, fill = "white", col = "black") + 
  facet_grid(Signal ~ smooth, labeller = label_parsed) + theme_bw() +
  theme(text = element_text(size = 16)) +  xlim(c(0, 6)) + 
  xlab("Number of Clusters") + ggtitle("(a) Design 1")


p2data <- rbind(design2weakSummary$finalK, design2strongSummary$finalK) %>%
  mutate(Signal = rep(c("Weak", "Strong"), each = 5 * N_SIMU_REPS))
p2data$Signal <-  factor(p2data$Signal, levels = c("Weak", "Strong"),
                         labels = c("Weak", "Strong"))
p2 <- p2data %>% ggplot(aes(x = count)) + 
  geom_histogram(binwidth = 0.5, fill = "white", col = "black") + 
  facet_grid(Signal ~ smooth, labeller = label_parsed) + theme_bw() +
  theme(text = element_text(size = 16)) +  xlim(c(0, 6)) + 
  xlab("Number of Clusters") + ggtitle("(b) Design 2")
```


(ref:Khistlorenz) Histogram of number of clusters inferred by the proposed
method using Lorenz curves for each state under the two designs with two signal strengths.

```{r fig.align='center', fig.cap="(ref:Khistlorenz)", message=FALSE,fig.height=7,fig.width = 8, results="hide"}
gridExtra::grid.arrange(p1, p2, ncol = 1)
```


(ref:realdatadesc)  Descriptive statistics for PUMS data, visualized on US
map: (a) Gini coeﬃcient; (b) state median income.

```{r fig.align = 'center', fig.cap="(ref:realdatadesc)", message=FALSE,fig.height = 10, fig.width = 7.5}
index <- unique(data$data.ST)
medincome <- map_dbl(index, ~median(data$data.HINCP[data$data.ST == .x]))
Gini_coefficient <- rep(0, length(index))
for (i in seq_along(index)) {
  Gini_coefficient[i] = Gini(data$data.HINCP[data$data.ST == index[i]])
}
stateinfo <- stateinfo %>% mutate(fips = as.numeric(fips)) %>%
  mutate(Gini = Gini_coefficient) %>%
  mutate(medincome = medincome)

gini <- plot_usmap(data = stateinfo, value = "Gini", labels = TRUE) +
  scale_fill_continuous(low = "white", high = "#004D40", name = "Gini coefficient") +
  ggtitle("(a)")

income <- plot_usmap(data = stateinfo, value = "medincome", labels = TRUE) +
  scale_fill_continuous(low = "white", high = "#004D40", name = "Median income") +
  ggtitle("(b)")
gridExtra::grid.arrange(gini, income, ncol = 1)
```




(ref:realdatacluster) Illustration of three clusters identiﬁed by the proposed
method for 51 states.



```{r fig.align='center', fig.cap = "(ref:realdatacluster)", message = FALSE, fig.height = 5, fig.width=7.5}
m <- length(index)
lorenzcurve <- matrix(0, 1000, m)
for (i in seq_along(index)) {
  lorenzcurve[, i] <-
    quantile(Lc(data$data.HINCP[data$data.ST == index[i]])$L, seq(0.001, 1, by =
                                                                    0.001))
}

stateinfo <- stateinfo %>% mutate(fips = as.numeric(fips)) %>%
  mutate(Gini = Gini_coefficient)


srsf <- f_to_srvf(lorenzcurve, seq(0.001, 1, by = 0.001))

inner_prod_matrix <- matrix(0, m, m)
for (i in 1:m) {
  for (j in 1:m) {
    inner_prod_matrix[i, j] = trapz(seq(0.001, 1, by = 0.001), srsf[, i] * srsf[, j])
  }
}

n <- 51
A <- log((inner_prod_matrix - min(inner_prod_matrix)) / (max(inner_prod_matrix) -
                                                           inner_prod_matrix))
A[which(A == Inf)] = max(A[which(is.finite(A) == T)])
A[which(A == -Inf)] = min(A[which(is.finite(A) == T)])
AAA <- A; AAA[lower.tri(AAA)] <- 0

set.seed(100)
clusFit <-  CDMFM(data = A, data1 = AAA, lambda1 = 3, neighbour = 3,
            distance = distance, niterations = N_MAX_ITER, mu_0 = max(A),
            mu_0off = min(A), t_0 = 2, alpha = 1, beta = 1, GAMMA = 1,
            LAMBDA = 1, initNClusters = 9)
finalClusers <- getDahl(clusFit, 200)
stateinfo$cluster <- as.factor(finalClusers$zout)

plot_usmap(data = stateinfo, values = "cluster", labels = TRUE) + 
  scale_fill_manual(values = cbPalette, name = "Cluster")
```

(ref:realdatalorenz) Average Lorenz curves for states in the three identiﬁed
clusters.


```{r fig.align='center', fig.cap = "(ref:realdatacluster)", message = FALSE, fig.height = 5, fig.width=7.5}
results <- finalClusers$zout
temp1 <- rowMeans(lorenzcurve[, which(results == 1)])
temp2 <- rowMeans(lorenzcurve[, which(results == 2)])
temp3 <- rowMeans(lorenzcurve[, which(results == 3)])
temp4 <- rowMeans(lorenzcurve[, which(results == 4), drop = FALSE])

segment_data <- data.frame(x = 0, xend = 1, y = 0, yend = 1)

toplot <- data.frame(value = c(temp1, temp2, temp3, temp4), 
                     Cluster = rep(c("Cluster 1", "Cluster 2", "Cluster 3", "Cluster 4"),
                                   each = 1000),
                     x = rep(1:1000, 4)/1000)

cbPalette <- c("#999999", "#E69F00", "#56B4E9", "#009E73", "#F0E442",
               "#0072B2", "#D55E00", "#CC79A7")


(toplot %>% ggplot(aes(x = x, y = value, group = Cluster, col = Cluster, lty = Cluster)) +
  geom_line() + theme_bw() + 
  theme(panel.grid = element_blank()) + 
  xlab("% of objects") + ylab("% of regarded variable") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.2)) + 
  scale_y_continuous(breaks = seq(0, 1, by = 0.2)) + 
  geom_segment(data = segment_data, aes(x = x, y = y, xend = xend, yend = yend), color = "blue",
                inherit.aes = FALSE) + 
  theme(legend.position = c(0.15, 0.8),
        legend.background = element_rect(color = 'black', fill = 'white', linetype = 'solid')) +
  coord_fixed() + theme(text = element_text(size = 16)) + 
  scale_color_manual(values = cbPalette) )

```


# Replication for Table 2

Table 2 (performance comparison) is replicated in this section.

```{r message = FALSE, warning = FALSE, results = "hide"}
### Kmeans

weak1final <- which.max(design1weakSummary$correctK) - 1
weak1 <- design1weakSummary$finalK$count[(N_SIMU_REPS * weak1final + 1):(N_SIMU_REPS * weak1final + N_SIMU_REPS)]
Kmeans.weak1 <- purrr::map(1:N_SIMU_REPS,  .f = function(x) {
  set.seed(x)
  temp <- kmeans(t(design1weak[[x]]$srvf),
                 centers = weak1[x])
  return(temp$cluster)
})
RIweak1 <- mean(map_dbl(Kmeans.weak1, ~fossil::rand.index(.x, IND1)))

strong1final <- which.max(design1strongSummary$correctK) - 1
strong1 <- design1strongSummary$finalK$count[(N_SIMU_REPS * strong1final + 1):(N_SIMU_REPS * strong1final + N_SIMU_REPS)]
Kmeans.strong1 <- purrr::map(1:N_SIMU_REPS,  .f = function(x) {
  set.seed(x)
  temp <- kmeans(t(design1strong[[x]]$srvf),
                 centers = strong1[x])
  return(temp$cluster)
})
RIstrong1 <- mean(map_dbl(Kmeans.strong1, ~fossil::rand.index(.x, IND1)))

weak2final <- which.max(design2weakSummary$correctK) - 1
weak2 <- design2weakSummary$finalK$count[(N_SIMU_REPS * weak2final + 1):(N_SIMU_REPS * weak2final + N_SIMU_REPS)]
Kmeans.weak2 <- purrr::map(1:N_SIMU_REPS,  .f = function(x) {
  set.seed(x)
  temp <- kmeans(t(design2weak[[x]]$srvf),
                 centers = weak2[x])
  return(temp$cluster)
})
RIweak2 <- mean(map_dbl(Kmeans.weak2, ~fossil::rand.index(.x, IND2)))

strong2final <- which.max(design2strongSummary$correctK) - 1
strong2 <- design2strongSummary$finalK$count[(N_SIMU_REPS * strong2final + 1):(N_SIMU_REPS * strong2final + N_SIMU_REPS)]
Kmeans.strong2 <- purrr::map(1:N_SIMU_REPS,  .f = function(x) {
  set.seed(x)
  temp <- kmeans(t(design2strong[[x]]$srvf),
                 centers = strong2[x])
  return(temp$cluster)
})
RIstrong2 <- mean(map_dbl(Kmeans.strong2, ~fossil::rand.index(.x, IND2)))

### funcy

#################################################################################
#################################################################################

library(funcy)

results1weak <- list()
for (i in 1:N_SIMU_REPS) {
  if (weak1[i] > 1) {
    temp <- funcit(design1weak[[i]]$lorenzcurve, weak1[i], method = "fitfclust", seed = i)
    results1weak[[i]] <- Cluster(temp)
  } else {
    results1weak[[i]] <- rep(1, 51)
  }
}

fcweak1 <- mean(map_dbl(results1weak, ~fossil::rand.index(.x, IND1)))

results1strong <- list()
for (i in 1:N_SIMU_REPS) {
  if (strong1[i] > 1) {
    temp <- funcit(design1strong[[i]]$lorenzcurve, strong1[i], method = "fitfclust", seed = i)
    results1strong[[i]] <- Cluster(temp)
  } else {
    results1strong[[i]] <- rep(1, N_STATES)
  }
}

fcstrong1 <- mean(map_dbl(results1strong, ~fossil::rand.index(.x, IND1)))


results2weak <- list()
for (i in 1:N_SIMU_REPS) {
  if (weak2[i] > 1) {
    temp <- funcit(design2weak[[i]]$lorenzcurve, weak2[i], method = "fitfclust", seed = i)
    results2weak[[i]] <- Cluster(temp)
  } else {
    results2weak[[i]] <- rep(1, N_STATES)
  }
}

fcweak2 <- mean(map_dbl(results2weak, ~ fossil::rand.index(.x, IND2)))
 
results2strong <- list()
for (i in 1:N_SIMU_REPS) {
  if (strong2[i] > 1) {
    temp <- funcit(design2strong[[i]]$lorenzcurve, strong2[i], method = "fitfclust", seed = i)
    results2strong[[i]] <- Cluster(temp)
  } else {
    results2strong[[i]] <- rep(1, N_STATES)
  }
}

fcstrong2 <- mean(map_dbl(results2strong, ~fossil::rand.index(.x, IND2)))

output <- data.frame(rbind(
  c(mean(design1weakSummary$RImeans[weak1final + 1]),
    mean(design1strongSummary$RImeans[strong1final + 1]),
    mean(design2weakSummary$RImeans[weak2final + 1]),
    mean(design2strongSummary$RImeans[strong2final + 1])),
  c(RIweak1, RIstrong1, RIweak2, RIstrong2),
  c(fcweak1, fcstrong1, fcweak2, fcstrong2)
))
row.names(output) <- c("MRFC-MFM-fCluster", "K-means", "model-based")
colnames(output) <- c("Design 1 weak", "Design1 strong", "Design 2 weak", "Design 2 strong")
```

```{r}
knitr::kable(round(output, 3), booktabs = TRUE,
             caption = 'Comparison of final clustering performance using average RI over 100 simulation replicates.')
```